---
title: "F19 STA 100 A01 Discussion 01"
author: "Yishan Huang"
date: "2019/9/29"
output: html_document
---

Discussion Time: Tuesday 8:00 -- 8:50 am, Haring Hall 1204.

Notes: https://github.com/Hahahuo-13316/sta100-a01-fall19

Office Hour: Tuesday 2:00 -- 3:00 pm, Earth and Physical Science Building 1317.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting Started

### Install R

The latest version 3.6.1 of R can be found on its website https://www.r-project.org/. Click on **CRAN** on the left, and choose an appropriate mirror to download the install package. Follow the instruction and complete the installation.

### Choose an IDE

There are several IDE (integrated development environment) for R, one of the popular IDE is RStudio. In this discussion I will always use RStudio to present and run the codes. 

To install RStudio, go to their website https://rstudio.com/ and download the latest version. After installing that, you could go to preferences -- appearance to adjust the font, font size, theme, etc. of IDE.

In this discussion I will also use **R Markdown**, which is a tool in RStudio that could create HTML or PDF documents in which you can put codes, outputs and LaTeX formulas.

### When you need some help

You could use the documentation, which could be downloaded on https://cran.r-project.org/manuals.html. Or, just Google it to look for the command you need, then type **?+command** in the console (of your IDE) to know more about a specific command.

```{r}
?sum
?lm
```

## R Introduction

### Basics
$x^2+y^2$
You could use # to make comments on your R code:
```{r}
# put # on a line to create a comment
```

Assign values to variables. Notice that '<-' and '=' have the same meaning, but '<-' is recommanded in R. Notice that for commands in console, 'print' could be omitted.
```{r}
x <- 2
x
y = 4
y
print(y)
```

Let's go through some basic operations:
```{r}
x + y         #addition
x - y         #subtraction
-x            #negation
x * y         #multiplication
x / y         #division
x^y           #powers
log(x)        #natural log
exp(x)        #exponentiation
sqrt(x)       #square root
x == 4        #equality
x >= 4        #greater than or equal
x > 4         #greater than
x != 4        #not equals
!TRUE         #logical negation
```

### Vectors
Use c(...) to create a vector:
```{r}
v <- c(1, 2, 3, 4, 5, 6)
u <- c(7, 10, 15, 30, 40, 45)
u
v
```
Basic operations for vectors are **element-wise**:
```{r}
u + v
u - v
-u
u * v
u / v
u^v
log(v)
exp(v)
```
And also there are operations between vector and scalar:
```{r}
v - 1
1 / v
v^2
2^v
```
Access specific element in a vector using index, or get slices. Notice that **the index begin with 1**.
```{r}
u[1]
u[1:3]
```

### Statistical discription of vectors
```{r}
x <- c(1, 1, 1, 2, 2, 2)
sum(x)		  #sum
length(x)		#number of entries
mean(x)			#mean
sum(x) / length(x) == mean(x)
```

### Random number and random sample
```{r}
runif(10, min = 0, max = 100)
sample(1:1000, size = 12)
```

### Flow control
There are for and while loops in R:
```{r}
for(i in 1:10) {
  print(i)
}
```

```{r}
i <- 1
while(i <= 10) {
  print(i)
  i <- i + 1
}
```

**Important notice:** in R, do not use loop if there exists corresponding vectorised methods. For example, it is much slower to run the following code
```{r}
system.time({
  s <- 0
  for(i in 1:123456789) {
    s <- s + i
  }
  s
})
```
than simply use 'sum'.
```{r}
system.time({sum(1:123456789)})
```